Project1_RM_Objective_1

### 2020-02-16 WorkingCode/Project1_RM_Objective_1.Rmd
Add files via upload

#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
nyc <- select(nyc, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood_group"))

@@

#Checking for NAs
#md.pattern(nyc)
#Drop NAs that are present
nyc <- na.omit(nyc)
#Confirming NA drop
#nrow(nyc)

@@

@@

#Linearity check of linear-linear data set
#pairs(nyc,col=nyc$neighbourhood) #Color by neighborhood
```

@@

#Linearity check of log-linear data set
#pairs(log.nyc,col=log.nyc$neighbourhood)
```

@@

#Linearity Check of log-log data set
#pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood) #Color by neighborhood
```

@@

TEST/TRAIN CREATION
```{r create 90/10 train/test splits for each data source}
set.seed(100)

#nyc
index<-sample(1:dim(linear.nyc)[1],nrow(linear.nyc)*.9,replace=F)
linear.train<-linear.nyc[index,]
linear.test<-linear.nyc[-index,]

#log.nyc
index<-sample(1:dim(log.nyc)[1],nrow(log.nyc)*.9,replace=F)
log.train<-log.nyc[index,]
log.test<-log.nyc[-index,]
```

INTUITIVE LINEAR - LINEAR
```{r intuitive model building - linear}
#LINEAR - LINEAR
linear.intuitive.train.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.train)
linear.intuitive.predictions <- linear.intuitive.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.intuitive.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.intuitive.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.intuitive.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.intuitive.predictions, linear.test$price)/mean(linear.test$price)

linear.intuitive.final.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(linear.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.intuitive.final.model)^2))
summary(linear.intuitive.final.model)
par(mfrow=c(2,2))
plot(linear.intuitive.final.model)
confint(linear.intuitive.final.model)
```

INTUITIVE LOG - LINEAR
```{r intuitive model building - log}
#LOG - LINEAR
log.intuitive.test.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.train)
log.intuitive.predictions <- log.intuitive.test.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.intuitive.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.intuitive.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.intuitive.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.intuitive.predictions, log.test$lprice)/mean(log.test$lprice)

log.intuitive.final.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood + room_type + neighbourhood:room_type, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(log.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(log.intuitive.final.model)^2))
summary(log.intuitive.final.model)
par(mfrow=c(2,2))
plot(log.intuitive.final.model)
confint(log.intuitive.final.model)
```

@@

FORWARD LINEAR
```{r forward selection model - linear}
#FORWARD LINEAR
set.seed(77)

linear.forward.select.model = regsubsets(price~neighbourhood + room_type + neighbourhood:room_type + minimum_nights + number_of_reviews + calculated_host_listings_count + availability_365 + minimum_nights:number_of_reviews + minimum_nights:calculated_host_listings_count + number_of_reviews:calculated_host_listings_count + availability_365:minimum_nights + availability_365:number_of_reviews + availability_365:calculated_host_listings_count + tsquare_distance:minimum_nights + tsquare_distance:number_of_reviews + tsquare_distance:calculated_host_listings_count + tsquare_distance:availability_365,data=linear.train,method="forward",nvmax=500)

@@

linear.forward.train.model <-lm(price~neighbourhood + number_of_reviews + minimum_nights + calculated_host_listings_count + room_type + tsquare_distance,data=linear.train)
linear.forward.predictions <- linear.forward.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.forward.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.forward.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.forward.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.forward.predictions, linear.test$price)/mean(linear.test$price)

linear.forward.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.forward.final.model))
print("Full Model BIC: ")
print(BIC(linear.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.forward.final.model)^2))
summary(linear.forward.final.model)
par(mfrow=c(2,2))
plot(linear.forward.final.model)
```

FORWARD LOG
```{r forward selection model - log}
#FORWARD LOG
set.seed(77)

log.forward.select.model = regsubsets(lprice~.,data=log.train,method="forward",nvmax=500)

@@

log.forward.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.forward.predictions <- log.forward.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.forward.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.forward.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.forward.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.forward.predictions, log.test$lprice)/mean(log.test$lprice)

log.forward.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.forward.final.model))
print("Full Model BIC: ")
print(BIC(log.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.forward.final.model)^2))
summary(log.forward.final.model)
par(mfrow=c(2,2))
plot(log.forward.final.model)
```

BACKWARD LINEAR
```{r backward selection model - linear}
set.seed(77)

linear.backward.select.model = regsubsets(price~.,data=linear.train,method="backward",nvmax=500)

@@

linear.backward.train.model <-lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
linear.backward.predictions <- linear.backward.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.backward.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.backward.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.backward.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.backward.predictions, linear.test$price)/mean(linear.test$price)

linear.backward.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.backward.final.model))
print("Full Model BIC: ")
print(BIC(linear.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.backward.final.model)^2))
summary(linear.backward.final.model)
par(mfrow=c(2,2))
plot(linear.backward.final.model)
```

BACKWARD LOG
```{r backward selection model - log}
set.seed(77)

log.backward.select.model = regsubsets(lprice~.,data=log.train,method="backward",nvmax=500)

@@

log.backward.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.backward.predictions <- log.backward.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.backward.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.backward.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.backward.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.backward.predictions, log.test$lprice)/mean(log.test$lprice)

log.backward.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.backward.final.model))
print("Full Model BIC: ")
print(BIC(log.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.backward.final.model)^2))
summary(log.backward.final.model)
par(mfrow=c(2,2))
plot(log.backward.final.model)
```

SEQREP LINEAR
```{r seqrep selection model - linear}
set.seed(77)

linear.seqrep.select.model = regsubsets(price~.,data=linear.train,method="seqrep",nvmax=500)

@@

linear.seqrep.train.model <-lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
linear.seqrep.predictions <- linear.seqrep.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.seqrep.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.seqrep.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.seqrep.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.seqrep.predictions, linear.test$price)/mean(linear.test$price)

linear.seqrep.final.model <- lm(price~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(linear.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.seqrep.final.model)^2))
summary(linear.seqrep.final.model)
par(mfrow=c(2,2))
plot(linear.seqrep.final.model)
```

@@

log.seqrep.train.model <-lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.seqrep.predictions <- log.seqrep.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.seqrep.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.seqrep.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.seqrep.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.seqrep.predictions, log.test$lprice)/mean(log.test$lprice)

log.seqrep.final.model <- lm(lprice~neighbourhood+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(log.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(log.seqrep.final.model)^2))
summary(log.seqrep.final.model)
par(mfrow=c(2,2))
plot(log.seqrep.final.model)
```

>>>>

#Dropping logical irrelevant variables: "id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighborhood"
nyc <- select(nyc, -c("id", "name", "host_id", "host_name", "last_review", "latitude", "longitude", "neighbourhood"))

@@

#Checking for NAs
md.pattern(nyc)
#Drop NAs that are present
nyc <- na.omit(nyc)
#Confirming NA drop
nrow(nyc)

@@

nyc <- filter(nyc, neighbourhood_group != "Staten Island")

@@

#Linearity check of linear-linear data set
#pairs(nyc,col=nyc$neighbourhood_group) #Color by neighborhood
```

@@

#Linearity check of log-linear data set
#pairs(log.nyc,col=log.nyc$neighbourhood_group)
```

@@

#Linearity Check of log-log data set
#pairs(log.indep.nyc,col=log.indep.nyc$neighbourhood_group) #Color by neighborhood
```

@@

TEST/TRAIN CREATION
```{r create 70/30 train/test splits for each data source}
set.seed(1234)

#nyc
index<-sample(1:dim(linear.nyc)[1],nrow(linear.nyc)*.7,replace=F)
linear.train<-linear.nyc[index,]
linear.test<-linear.nyc[-index,]

#log.nyc
index<-sample(1:dim(log.nyc)[1],nrow(log.nyc)*.7,replace=F)
log.train<-log.nyc[index,]
log.test<-log.nyc[-index,]
```

INTUITIVE LINEAR - LINEAR
```{r intuitive model building - linear}
#LINEAR - LINEAR
linear.intuitive.train.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = linear.train)
linear.intuitive.predictions <- linear.intuitive.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.intuitive.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.intuitive.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.intuitive.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.intuitive.predictions, linear.test$price)/mean(linear.test$price)

linear.intuitive.final.model <- lm(price ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(linear.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.intuitive.final.model)^2))
summary(linear.intuitive.final.model)
par(mfrow=c(2,2))
plot(linear.intuitive.final.model)
confint(linear.intuitive.final.model)
```

INTUITIVE LOG - LINEAR
```{r intuitive model building - log}
#LOG - LINEAR
log.intuitive.test.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = log.train)
log.intuitive.predictions <- log.intuitive.test.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.intuitive.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.intuitive.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.intuitive.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.intuitive.predictions, log.test$lprice)/mean(log.test$lprice)

log.intuitive.final.model <- lm(lprice ~ minimum_nights + number_of_reviews + tsquare_distance + neighbourhood_group + room_type + neighbourhood_group:room_type, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.intuitive.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.intuitive.final.model))
print("Full Model BIC: ")
print(BIC(log.intuitive.final.model))
print("Full Model RSS: ")
print(sum(resid(log.intuitive.final.model)^2))
summary(log.intuitive.final.model)
par(mfrow=c(2,2))
plot(log.intuitive.final.model)
confint(log.intuitive.final.model)
```

@@

FORWARD LINEAR
```{r forward selection model - linear}
#FORWARD LINEAR
linear.forward.select.model = regsubsets(price~.,data=linear.train,method="forward",nvmax=20)

@@

linear.forward.train.model <-lm(price~neighbourhood_group + number_of_reviews + minimum_nights + calculated_host_listings_count + room_type + tsquare_distance,data=linear.train)
linear.forward.predictions <- linear.forward.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.forward.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.forward.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.forward.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.forward.predictions, linear.test$price)/mean(linear.test$price)

linear.forward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.forward.final.model))
print("Full Model BIC: ")
print(BIC(linear.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.forward.final.model)^2))
summary(linear.forward.final.model)
par(mfrow=c(2,2))
plot(linear.forward.final.model)
```

FORWARD LOG
```{r forward selection model - log}
#FORWARD LOG
log.forward.select.model = regsubsets(lprice~.,data=log.train,method="forward",nvmax=500)

@@

log.forward.train.model <-lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.forward.predictions <- log.forward.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.forward.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.forward.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.forward.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.forward.predictions, log.test$lprice)/mean(log.test$lprice)

log.forward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.forward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.forward.final.model))
print("Full Model BIC: ")
print(BIC(log.forward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.forward.final.model)^2))
summary(log.forward.final.model)
par(mfrow=c(2,2))
plot(log.forward.final.model)
```

BACKWARD LINEAR
```{r backward selection model - linear}
linear.backward.select.model = regsubsets(price~.,data=linear.train,method="backward",nvmax=500)

@@

linear.backward.train.model <-lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
linear.backward.predictions <- linear.backward.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.backward.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.backward.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.backward.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.backward.predictions, linear.test$price)/mean(linear.test$price)

linear.backward.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.backward.final.model))
print("Full Model BIC: ")
print(BIC(linear.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.backward.final.model)^2))
summary(linear.backward.final.model)
par(mfrow=c(2,2))
plot(linear.backward.final.model)
```

BACKWARD LOG
```{r backward selection model - log}
log.backward.select.model = regsubsets(lprice~.,data=log.train,method="backward",nvmax=500)

@@

log.backward.train.model <-lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.backward.predictions <- log.backward.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.backward.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.backward.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.backward.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.backward.predictions, log.test$lprice)/mean(log.test$lprice)

log.backward.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.backward.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.backward.final.model))
print("Full Model BIC: ")
print(BIC(log.backward.final.model))
print("Full Model RSS: ")
print(sum(resid(log.backward.final.model)^2))
summary(log.backward.final.model)
par(mfrow=c(2,2))
plot(log.backward.final.model)
```

SEQREP LINEAR
```{r seqrep selection model - linear}
linear.seqrep.select.model = regsubsets(price~.,data=linear.train,method="seqrep",nvmax=500)

@@

linear.seqrep.train.model <-lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=linear.train)
linear.seqrep.predictions <- linear.seqrep.train.model %>% predict(linear.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(linear.seqrep.predictions, linear.test$price))
print("Test Root Mean Square Error: ")
print(RMSE(linear.seqrep.predictions, linear.test$price))
print("Test Mean Absolute Error: ")
print(MAE(linear.seqrep.predictions, linear.test$price))
print("Prediction Error Rate: ")
RMSE(linear.seqrep.predictions, linear.test$price)/mean(linear.test$price)

linear.seqrep.final.model <- lm(price~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = linear.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(linear.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(linear.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(linear.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(linear.seqrep.final.model)^2))
summary(linear.seqrep.final.model)
par(mfrow=c(2,2))
plot(linear.seqrep.final.model)
```

@@

log.seqrep.train.model <-lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance,data=log.train)
log.seqrep.predictions <- log.seqrep.train.model %>% predict(log.test)
print("")
print("Test Adjusted R Squared: ")
print(R2(log.seqrep.predictions, log.test$lprice))
print("Test Root Mean Square Error: ")
print(RMSE(log.seqrep.predictions, log.test$lprice))
print("Test Mean Absolute Error: ")
print(MAE(log.seqrep.predictions, log.test$lprice))
print("Prediction Error Rate: ")
RMSE(log.seqrep.predictions, log.test$lprice)/mean(log.test$lprice)

log.seqrep.final.model <- lm(lprice~neighbourhood_group+number_of_reviews+minimum_nights+calculated_host_listings_count+room_type+tsquare_distance, data = log.nyc)
print("Full Model Adjusted R Squared: ")
print(summary(log.seqrep.final.model)$adj.r.squared)
print("Full Model AIC: ")
print(AIC(log.seqrep.final.model))
print("Full Model BIC: ")
print(BIC(log.seqrep.final.model))
print("Full Model RSS: ")
print(sum(resid(log.seqrep.final.model)^2))
summary(log.seqrep.final.model)
par(mfrow=c(2,2))
plot(log.seqrep.final.model)
```
